Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-11 providence/sections/workload.tex
more

\begin{figure}
\includegraphics[width=.5\textwidth]{optimal_workload_precinct_workload_ratio.png}
\caption{The optimal average workload of the audits we simulated using workload function \ref{eq:round_and_precinct_workload} for varying $w_p$, given as a fraction of the value for \Providence}
\label{fig:optimal_workload_precinct_workload_ratio}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=.5\textwidth]{optimal_workload_precinct_workload_ratio.png}
\caption{The optimal average workload of the audits we simulated using the workload Equation~\ref{eq:round_and_precinct_workload} for varying $w_p$, given as a fraction of the value for \Providence. Similar to Figure~\ref{optimal_workloads}, we show a generous range of values for the workload variable, $c_p$ in this case. If the time for a single ballot is $75$ seconds, then $c_p=50$ corresponds to over an hour of extra time to sample a ballot from a new container.}
\label{fig:optimal_workload_precinct_workload_ratio}
\end{figure}
